MSE and dynamic state variable model with sigma function

### 2018-06-26 doc/MSE_MAR_18.tex
updated modifications in doc and figures

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catches.eps} 
\caption{Caches- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Yields.eps} 
\caption{Yields- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Selectivity.eps} 
\caption{Changes in selectivity- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Effort.eps} 
\caption{Effort- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catchesbyarea.eps} 
\caption{Caches by area- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Economics.eps} 
\caption{Revenues- Prices of the two species are equal (a truly mixed fishery)}
\end{figure}
%---

\newpage
\section{Discussion}
\label{sec4}
tbd
prellezo 2016, In the mid-term and without any consideration made in terms of the ecosystem functioning as a whole, the results obtained from applying any kind of exemption or flexibility are, simply, negative. Fishing beyond FMSY (even in one year) implies that there will be a penalty in the future. This penalty will come in the form of lower biomasses, that has the mixed effect of increasing the cost of fishing the same level of catches and reducing the total catch due to the lower abundances and the subsequent lower TACs.

>>>>

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catches.eps} 
\caption{Modelled total annual catches (thousand tonnes) for all vessels for both (a,c) species 1 and (b,d) species 2 in relation to the available individual quota (red line). In panels (a,b) only species 1 quota constrained the fishery, while in (c,d) both species quota constrained the fishery. MP year reflects the year where the management plan was introduced}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Yields.eps} 
\caption{Modelled yield per recruitment curves (thousand tonnes) for both (a,c) species 1 and (b,d) species 2 in relation to the management plan period (black line: period before the MP; grey line: period after the introduction of the MP). (a,c,d) After the introduction of the MP all species are underharvested to reach Fmsy, while in (b) species 2 is overharvested due to the abscence of any quota restriction.}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Selectivity.eps} 
\caption{Modelled changes in selectivity for both (a,c) species 1 and (b,d) species 2 in relation to the catch decision options made based in the availble individual quota. In panels (a,b) only species 1 quota constrained the fishery, while in (c,d) both species quota constrained the fishery. Black lines: selectivity curve before the MP period; grey line: selectivity curve after the introduction of the MP.}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Effort.eps} 
\caption{Modelled spatial allocation of effort per year (\%) when (a) only species 1 has quota limitations and (d) both species are quota limited.  MP years reflect the year where the management plan was introduced. Panels (b-c) and (e-f) are the average monthly effort (days/month). Panels (b,e) are based on the 3 years monthly effort average (days) before the introduction of the MP, while (b,e) are the 3 years monthly effort average based on the period after the introduction of the MP.}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Catchesbyarea.eps} 
\caption{Modelled catches (thousand tonnes/year) by area (blue line: Northern area, red line: Southern area) for both (a,c) species 1 and (b,d) species 2 in relation to the management plan period. In panels (a,b) only species 1 quota constrained the fishery, while in (c,d) both species quota constrained the fishery. MP year reflects the year where the management plan was introduced.}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Economics.eps} 
\caption{Modelled main economics (thousand euro/ year) for the fleet under the management scenarios: (a-c) when the fishery is quota contrained only by species 1, while (d-f) both species constrained the fishery. Panels (a,d) and (b,e) shown the average annual net and grooss revenues, respectively, by vessel. MP year reflects the year where the management plan was introduced. Trade-offs between net revenue (black lline), gross revenue (grey line), fuel cost (blue line) and annual fines (red line) for the fleet are shown in panels (c,f).}
\end{figure}
%---

\clearpage

\section{Discussion}
\label{sec4}
tbd
prellezo 2016, In the mid-term and without any consideration made in terms of the ecosystem functioning as a whole, the results obtained from applying any kind of exemption or flexibility are, simply, negative. Fishing beyond FMSY (even in one year) implies that there will be a penalty in the future. This penalty will come in the form of lower biomasses, that has the mixed effect of increasing the cost of fishing the same level of catches and reducing the total catch due to the lower abundances and the subsequent lower TACs.
